An Analysis of Performance Bottlenecks in MRI Pre-Processing

### 2024-04-17 paper/paper.tex
[ADD] link to ITK issue.

After further analysis of the ANTs registrationSyN single-precision pipeline, we found that the template\footnote{\href{https://github.com/InsightSoftwareConsortium/ITK/blob/d9c585d96359bf304ad3047148cee81bf27ac0c1/Modules/Core/ImageFunction/include/itkVectorInterpolateImageFunction.h\#L46-L48}{itkVectorInterpolateImageFunction.h}} forces the output of its function to be in double precision, with it's \textit{EvaluateAtContinuousIndex} contributing most of the CPU time. Therefore, the pipeline wastes CPU cycles to convert the input data to double in ITK, and potentially to cast back to float in ANTS. We think this bug causes the slow-down. We tried recompiling a version of ITK to fix this issue, but we were unsuccessful due to the size and complexity of the code base. This example shows that the use of reduced precision is not trivial and require a deep understanding of the code base. Moreover, benchmark should be performed to ensure that the reduced precision does not impact the performance or accuracy of the pipeline.
We reported the issue on ITK GitHub repository at: \href{}{} \MD{TODO open issue}

@@

Our profiling results from VTune are publicly available at:
\\\href{URL}{\MD{TODO add Zenodo link}}
% Waiting on data transfer from Compute Canada

>>>>

After further analysis of the ANTs registrationSyN single-precision pipeline, we found that the template\footnote{\href{https://github.com/InsightSoftwareConsortium/ITK/blob/d9c585d96359bf304ad3047148cee81bf27ac0c1/Modules/Core/ImageFunction/include/itkVectorInterpolateImageFunction.h\#L46-L48}{itkVectorInterpolateImageFunction.h}} forces the output of its function to be in double precision, with it's \textit{EvaluateAtContinuousIndex} contributing most of the CPU time. Therefore, the pipeline wastes CPU cycles to convert the input data to double in ITK, and potentially to cast back to float in ANTS. We think this bug causes the slow-down. We tried recompiling a version of ITK to fix this issue, but we were unsuccessful due to the size and complexity of the code base. This example shows that the use of reduced precision is not trivial and require a deep understanding of the code base. Moreover, benchmark should be performed to ensure that the reduced precision does not impact the performance or accuracy of the pipeline. We reported the issue on ITK GitHub repository (see issue \#4593)~\footnote{\href{https://github.com/InsightSoftwareConsortium/ITK/issues/4593}{https://github.com/InsightSoftwareConsortium/ITK/issues/4593}}.

@@

Our profiling results from VTune are publicly available at:
\\\href{https://doi.org/10.5281/zenodo.10987491}{https://doi.org/10.5281/zenodo.10987491}
\MD{TODO finalize the metadata entry and publish}
